### 2012-10-11 Docs/architecture/architecture.tex
fix compilation

      A runtime parameter, {\tt use\_eos_coulomb}, is defined in
      this EOS to enable/disable Coulomb corrections.

@@

The thermodynamic quantities are stored in a Fortran type {\tt eos\_t},
which has fields for all the thermodynamic inputs and outputs.  The 
type definition is brought in through {\tt eos\_type\_module}.
\footnote{ Note: an older interface to the EOS exists, but is
  deprecated.  In this mode, the {\tt eos\_old_interface} module declares 
  the variables that need appear in the old-style {\tt eos} call
  argument list.  \maestro\ routines use these module variables in the
  EOS call to avoid having to declare each quantity in each routine
  that calls the EOS.  Most code has been updated to use the new interface.}

>>>>

      A runtime parameter, {\tt use\_eos\_coulomb}, is defined in
      this EOS to enable/disable Coulomb corrections.

@@

The thermodynamic quantities are stored in a Fortran type {\tt eos\_t},
which has fields for all the thermodynamic inputs and outputs.  The 
type definition is brought in through {\tt eos\_type\_module}.
\footnote{ Note: an older interface to the EOS exists, but is
  deprecated.  In this mode, the {\tt eos\_old\_interface} module declares 
  the variables that need appear in the old-style {\tt eos} call
  argument list.  \maestro\ routines use these module variables in the
  EOS call to avoid having to declare each quantity in each routine
  that calls the EOS.  Most code has been updated to use the new interface.}
